Equalizer 2\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Final Collage results
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@51 db7c848b-7755-4df2-b763-8796797afa52

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/daviddist}
  \caption{\label{fDavidDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the David 2mm data set in
    \fig{fDavid2mm}}
\end{figure*}

@@

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/spikesdist}
  \caption{\label{fSpikesDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the spike data set in
    \fig{fVolumes}, left}
\end{figure*}

@@

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/beechnutdist}
  \caption{\label{fBeechnutDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the beechnut data set in
    \fig{fVolumes}, right}
\end{figure*}

@@

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/ifdist}
  \caption{\label{fIFDist}Object synchronization using different network
    transports}
\end{figure*}

@@

Our RSP multicast implementation performs as expected. \textsf{Collage} starts
using multicast to commit new object versions when two or more clients are
mapped, since the transmission to a single client is better done using unicast.
RSP consistently outperforms unicast on the same physical interface and shows
good scaling behavior (2.5 times slower on 16 vs 2 clients on ethernet, 1.8
times slower on InfiniBand). The scaling is significantly better when only one
process per node is used (\fig{fIFDist}, middle: 30\% slower on ethernet, flat
on InfiniBand). The increased transmission time with multiple clients is caused
by a higher probability of packet loss, which increases significantly when using
more than one process per node, as shown in \fig{fIFDist}, right. Infiniband
outperforms ethernet slightly, but is largely limited by the RSP implementation
throughput of preparing and queueing the datagrams to and from the protocol
thread, which we observed in a profiling analysis.

>>>>

@@

@@

@@

@@

Our RSP multicast implementation performs as expected. \textsf{Collage} starts
using multicast to commit new object versions when two or more clients are
mapped, since the transmission to a single client is better done using unicast.
RSP consistently outperforms unicast on the same physical interface and shows
good scaling behavior (2.5 times slower on 16 vs 2 clients on ethernet, 1.8
times slower on InfiniBand). The scaling is significantly better when only one
process per node is used (\fig{fIFDist}, middle: 30\% slower on ethernet,
nearly flat on InfiniBand). The increased transmission time with multiple
clients is caused by a higher probability of packet loss, which increases
significantly when using more than one process per node, as shown in
\fig{fIFDist}, right. This figure plots the number of retransmissions
divided by the number of datagrams. Infiniband outperforms ethernet slightly,
but is largely limited by the RSP implementation throughput of preparing and
queueing the datagrams to and from the protocol thread, which we observed in a
profiling analysis.

\begin{figure*}[ht]\center
  \includegraphics[height=.19\textheight]{images/daviddist}
  \caption{\label{fDavidDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the David 2mm data set in
    \fig{fDavid2mm}}
\end{figure*}
\begin{figure*}[ht]\center
  \includegraphics[height=.19\textheight]{images/spikesdist}
  \caption{\label{fSpikesDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the spike data set in
    \fig{fVolumes}, left}
\end{figure*}
\begin{figure*}[ht]\center
  \includegraphics[height=.19\textheight]{images/beechnutdist}
  \caption{\label{fBeechnutDist}Object mapping (left) and data synchronization
    time (middle, detail view right) for the beechnut data set in
    \fig{fVolumes}, right}
\end{figure*}
\begin{figure*}[ht]\center
  \includegraphics[height=.19\textheight]{images/ifdist}
  \caption{\label{fIFDist}Object synchronization using different network
    transports}
\end{figure*}
\clearpage
